\Large \bf Frontrunning

### 2018-06-13 frontrunning/Latex/sections/paper.tex
[frontrunning] More on status ICO

\subsubsection{Status ICO}
In July 2017, Status.im did their ICO and they reached their cap, hence closing the ICO, within 3 hours, by collecting over 200 million dollars (300K Ether) worth of Ethereum ~\cite{statusicoanalysis}.
%NOTE: ICO Initial Coin Offering should be explained probably in introduction section. the process of ICO smart contract and how the capped system works --> limited time/funds can be included in the ico and why people would try to get in as soon as possible, explain how their investment strategy works and such. Maybe the second half could be explained here to say why frontrunning an ICO makes sense? 
% add more on capped ICOs, status used Distribution & Dynamic Ceilings : https://blog.status.im/distribution-dynamic-ceilings-e2f427f5cca  ~\cite{statuswhitepaper}

@@

>>>>

\subsubsection{Status ICO}
ICO, Initial Coin Offering, is one of the blockchain applications, specially blockchains such as Ethereum with smart contract capability. The common practice is to deploy a smart contract on the blockchain indicating the details of the ICO such as the trade ratio, when it starts and ends, and more details on how it will be capped.
In June 2017, Status.im started their ICO and within 3 hours they reached the dynamic ceiling in place that triggered the end of the ICO, summing in 300,000 ether in funds, estimated at more than 200 million dollars at the time of their ICO. ~\cite{statusicoanalysis}. The idea behind Dynamic Ceilings is to make it more costly for larger contributors,  in the form of transaction fees, which have to split their contributions to different addresses, with minimal impact to smaller contributors~\cite{statuswhitepaper}.
On the time of the ICO there were reports of Ethereum network being unusable and transactions were not confirming. Further study showed that some mining pools (\todo: define mining pool) could have been manipulating the network for their own profit.

%NOTE: ICO Initial Coin Offering should be explained probably in introduction section. the process of ICO smart contract and how the capped system works --> limited time/funds can be included in the ico and why people would try to get in as soon as possible, explain how their investment strategy works and such. Maybe the second half could be explained here to say why frontrunning an ICO makes sense? 
% add more on capped ICOs, status used Distribution & Dynamic Ceilings : https://blog.status.im/distribution-dynamic-ceilings-e2f427f5cca  ~\cite{statuswhitepaper}

@@

% Proof of f2pool involvement: https://etherscan.io/address/0x5fb8373bf5086fb38ef0fb686b3092145de0d1c1
% funds come from f2pool and refunds goes back to f2pool again
